%-------------------------
% Resume in Latex
% Author : Justin Chen
% Based off of: https://github.com/jakegut/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}



%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Justin Chen} \\ \vspace{1pt}
    \small 443-604-2058 $|$ \href{mailto:x@x.com}{\underline{chennickyjustin@gmail.com}} $|$ 
    \href{https://linkedin.com/in/chen-justin}{\underline{linkedin.com/in/chen-justin}} $|$
    \href{https://github.com/chen-justin}{\underline{github.com/chen-justin}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Maryland}{College Park, MD}
      {Bachelor of Science in Computer Science, Minor in Mathematics}{Aug 2016 -- May 2020}
      \resumeItemListStart
        \resumeItem {GPA: 3.6/4.0}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Chewy}{Boston, MA}
      {Software Engineer II - Project 49}{Oct 2022 - Present}
      \resumeItemListStart
        \resumeItem {Worked in a small team of 18 engineers to successfully launch first international expansion into Canada.}
        \resumeItem {Developed and maintain multiple services forked from the original code base.}
        \resumeItem {Upskilled myself in areas normally supported by release, site reliability, and cloud engineering so that I could unblock myself when faced with an issue anywhere in the stack.}
        \resumeItem {Collaborated with other teams to understand and refine initial requirements to create a technical design document detailing strategy to migrate and adapt existing business processes to support Canadian launch.}
        \resumeItem {Worked closely with leadership to craft estimates of development required and prioritized critical work to meet the project's goals and deadlines}
        \resumeItem {Onboarded and oversaw two contractors brought on in the middle of the project and delegated appropriate sprint tasks. Planned and coordinated releases for features necessary for initial go-live.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
    \resumeSubSubheading
      {Software Engineer II - Agent Experience Team}{Feb 2021 - Oct 2022}
      \resumeItemListStart
        \resumeItem {Migrated and modernized multiple legacy core business processes to be in-line with existing CI/CD processes and adopt failover strategies across multiple regions. Upskilled myself in Jenkins, Terraform, and AWS services.}
        \resumeItem {Contributed to architecting and delivering OCR 2.0 - a revamp of a core business process that handled inbound faxes from veterinarians. The deliverable increased processing speed of inbound faxes by 8x and simplified a complex multi-step process to a single process.}
        \resumeItem {Designed a React.JS application that integrated with Oracle Service Cloud CRM to manage prescription and authorizations. Implemented a solution that eventually reduced the average handle time of relevant interactions from an estimated average of 2.5 minutes to 40 seconds. }
        \resumeItem {Managed deployments for the Oracle Service Cloud Team; became a subject matter expert in the team's testing processes.}
      \resumeItemListEnd
%-------------------------------------------

    \resumeSubSubheading
      {Software Engineer I - Agent Experience Team}{Jun 2020 - Feb 2021}
      \resumeItemListStart
        \resumeItem {Maintained business processes to support Customer Service Tech.}
        \resumeItem {Delivered "Dynamic Message Banners", a feature that integrated with Oracle Service Cloud REST APIs to deliver broadcasts and announcements to customer service agents in real-time in an outlook-like interface.}
      \resumeItemListEnd


    \resumeSubheading
      {Johns Hopkins Applied Physics Laboratory}{Laurel, MD}
      {Software Engineering Intern}{Jun 2019 -- Aug 2019}
      \resumeItemListStart
        \resumeItem {Created a responsive, interactive, and configurable dashboard to display complex health data}
        \resumeItem {Used front-end technologies and libraries such as React.JS, Material-UI, and Plotly.JS; Backend used Java, Hibernate, and Spring}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{2048} $|$ \emph{Swift, Firebase, Git}}{}
        \resumeItemListStart
          \resumeItem {Built an iOS app derivative of 2048}
          \resumeItem {Features generalized board sizes, along with traditional 4x4 board size, user login, persistent scores, and score leaderboards.}
        \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Spyfall} $|$ \emph{React.JS, Typescript, Node.JS, Express.JS, Socket.IO}}{}
          \resumeItemListStart
            \resumeItem {Created an online version of tabletop game, Spyfall}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, PHP, Java, Python, HTML/CSS} \\
     \textbf{Frameworks}{: React, Node.js, JUnit, Material-UI} \\
     \textbf{Developer Tools}{: Git, Docker, Jenkins, VS Code, IntelliJ} \\
     \textbf{DevOps}{: AWS, Terraform, Serverless, Jest, CI/CD, Cypress}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
